\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage{cmbright}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage[sf]{libertine}
\usepackage{microtype}
\usepackage{paracol}
\usepackage{supertabular}
\usepackage{titlesec}
\usepackage[T1]{fontenc}
\hypersetup{colorlinks, urlcolor=black, linkcolor=black}

% Geometry
\geometry{hmargin=1.75cm, vmargin=2.5cm}
\setlength\columnsep{0.05\textwidth}
\setlength\parindent{0pt}
\setlength{\smallskipamount}{8pt plus 3pt minus 3pt}
\setlength{\medskipamount}{16pt plus 6pt minus 6pt}
\setlength{\bigskipamount}{24pt plus 8pt minus 8pt}

% Style
\pagestyle{empty}
\titleformat{\section}{\scshape\LARGE\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{\bigskipamount}{\smallskipamount}
\newcommand{\heading}[2]{{\sffamily\Huge #1}\\\smallskip{\large{#2}}}
\newcommand{\entry}[4]{{{\textbf{#1}}} \\ #3 \\ #2 \hfill #4}
\newcommand{\edentry}[3]{\textbf{#1} \\ #2 | #3}
\newcommand{\jobentry}[3]{\textbf{#1} \\ #2 \hfill #3}
\newcommand{\tableentry}[3]{\textsc{#1} & #2\expandafter\ifstrequal\expandafter{#3}{}{\\}{\\[6pt]}}

\begin{document}

\vspace*{\fill}

% Name & headline
\heading{Vinícius Ernani de Carvalho}{Senior Software Consultant}

Phone: +55 84 99147-9189 | GitHub: \href{www.github.com/erneani}{@erneani} \\
Email: \href{mailto:viniciusernanicarvalho@gmail.com}{viniciusernanicarvalho@gmail.com} | Linkedin: \href{www.linkedin.com/in/vinicius-ernani}{in/vinicius-ernani}

\begin{paracol}{2}

    \section{About me}
    
    Hi, I am Vinícius Ernani! I am a \textbf{Software Consultant} with experience in the \textbf{full cycle} of product development using many languages, tools, and frameworks. \\
    My focus over the last few years was to create \textbf{digital solutions} that implement \textbf{modern, reactive, and scalable architectures}.
    
    \switchcolumn
    
    \section{education}
    
    \edentry{Federal University of Rio Grande do Norte (UFRN)}{Computer Science}{2019 - 2024}

    \edentry{Federal Institute of Technology of Rio Grande do Norte (IFRN)}{Software Development}{2015 to 2019}
    
    \edentry{Digital Metropolis Institute (IMD)}{Web Development}{2017 to 2021}

\end{paracol}

\section{experience}

\jobentry{Thoughtworks}{Senior Software Consultant}{May/2021 - Now}

\smallskip

Joined Thoughtworks as a Software Consultant to comprehend business needs and deliver impact and value in the form of Software.

\medskip

\begin{paracol}{2}

    - Provided maintenance and scalability for a legacy and critical financial spreadsheet application for a US big Real Estate company. \\

    - Worked on the creation of a globally distributed mathematical application with real-time data for a US big Oil and Gas company. \\

    - Provided technical and business expertise to improve client retention for products in a big Oil and Gas company from the UK.

    \switchcolumn

    Some tools I use to perform this job are: \\
    - Front End Technologies (Angular and React); \\
    - Back End Technologies (FastAPI, Express, Spring Framework, and .NET); \\
    - FaaS (AWS Lambda and Azure Functions); \\
    - Git; \\
    - Databases (PostgreSQL and Redis); \\
    - Message Brokers (Kafka and RabbitMQ); \\
    - Code Quality services (SonarQube) and
    - Testing Tools (TDD, RTL, Pytest, Jest).

\end{paracol}

\medskip

\jobentry{Globoplay - Globo.com/Altran}{Front End SmartTV Developer}{Nov/2020 - May/2021}

\smallskip

Joined Globo.com to research and create solutions for the SmartTV environment at LATAM's biggest streaming company, the Globoplay.\\

\begin{paracol}{2}

    - Delivered secure, fast, and lightweight web components for a streaming platform with more than 5 million users, monthly. \\
    - Researched technologies to improve application usability and responsiveness using React and Canvas.
    
    \switchcolumn
    
    - Co-implemented a robust fallback system that increased the user screen time during peak hours. \\
    - Implemented an event-based architecture to get component information on the go. \\
    - Used GraphQL, React, Typescript, Canvas, and Redux.

\end{paracol}

\medskip

\jobentry{Retail Project - IMD/ASUS/FOXCONN}{Front End Researcher}{Jul/2020 - Nov/2020}

\smallskip

Joined an ASUS project as a Front End Researcher to architect the client side for an internal ASUS application.

\smallskip

\begin{paracol}{2}

    - Architected a React client application using a Design System. \\
    - Created a Notification System using Service Workers and Local Storage. \\
    - Was the Front End application leader, managing other researchers.
    
    \switchcolumn
    
    - Co-authored an internal lib for organizational rules involving Roles, Processes, and Permissions. \\
    - Worked with MobX, Typescript, React, CSS-in-JS, Python, and Django.

\end{paracol}

\medskip

\jobentry{B2Soft}{Front End Developer}{Mar/2019 - Mar/2020}

\smallskip

At B2Soft, my responsibility was to create user interfaces and usability designs to improve the usage of a delivery application.

\smallskip

\begin{paracol}{2}

    - Created a React Desktop system that listens to a stream of orders and displays them to the user in real time. \\
    - Worked on a Retail management application with an eye for accessibility for Illiterate customers. \\
    
    \switchcolumn
    
    - Implemented a React web application that was responsible for managing recent orders. \\
    - Implemented a Design System to unify the user experience between mobile, desktop, and web applications. \\
    - Worked with Redux, Typescript, Javascript, Python, Django, Electron, and React Native.

\end{paracol}

\jobentry{Ceará-Mirim City Hall}{System Analyst}{Aug/2018 - Dec/2018}

\smallskip

Joined the Ceará-Mirim City Hall as a System Analyst to create a lightweight web solution to integrate public schools to the internet using small, local configurable servers.

\smallskip

\begin{paracol}{2}

    - Created a lightweight Bootstrap-like library to style the application. \\
    - Worked on the accessibility team to research solutions for illiterate students to use the internet. \\

    \switchcolumn
    
    - Configured a Script to automatically raise local Tomcat Servers in local small servers. \\
    - Worked with PHP, HTML, CSS, Javascript, Docker, SQL, JQuery, ShellScript, and WordPress.

\end{paracol}

\begin{paracol}{2}

    \section{Languages}

    I have a strong interest in learning new languages and in communication. \\
    I am able to \textbf{communicate fluently} in \textbf{Portuguese} and \textbf{English}. \\
    I am able to \textbf{communicate, but not fluently} in \textbf{Spanish}. \\
    Actually, I am \textbf{learning French}.

    \switchcolumn

    \section{Interests}

    I am really into programming communities, so isn't unusual that I perform some talks on events from my local region. \\
    I am usually enrolled in a lot of things, like: \\

    - Go programming, \\
    - Functional Programming communities, \\
    - Computer Science Degree, \\
    - Game Development, and \\
    - Software Architecture communities.
    
\end{paracol}

\smallskip

Check also my \href{www.viniciusernani.com/}{personal website} and my \href{www.github.com/erneani}{GitHub profile}.

\end{document}